%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------
	\cventry
	{Software Developer} % Job title
	{Genoa Design International} % Organization
	{Mount Pearl, NL (Remote)} % Location
	{Oct 2022 - Jan 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Led and contributed to full-stack development, showcasing proficiency in software design, development, and deployment.}
			\item {Utilized key technologies: React for dynamic front-end, ASP.NET for backend, and SQL Server for efficient database management.}
			\item {Collaborated with cross-functional Agile teams to ensure effective project delivery and continuous integration.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Software Developer Intern} % Job title
	{Genoa Design International} % Organization
	{Mount Pearl, NL (Remote)} % Location
	{Jul 2022 - Aug 2022} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Engaged in a comprehensive software development internship, gaining hands-on experience with modern technologies.}
			\item {Assisted in various development tasks, laying the foundation for a successful transition to a full-time Software Developer role.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Financial Services Manager} % Job title
	{Bank of Montreal} % Organization
	{Stephenville, NL} % Location
	{May 2016 - June 2018} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Managed a portfolio of clients, providing expert advice on banking, lending, and investment solutions.}
			\item {Exceeded sales targets consistently for lending, investing, and everyday banking products.}
			\item {Opened and managed customer accounts, ensuring compliance with banking regulations.}
			\item {Advised clients on financial planning, tailoring solutions to meet their individual needs.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Front Desk Clerk} % Job title
	{Glynmill Inn} % Organization
	{Corner Brook, NL} % Location
	{Jun 2015 - Sep 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Performed night audit tasks, ensuring accurate balancing and closing of daily accounts.}
			\item {Managed guest check-ins, providing information about hotel services, charges, and facilities.}
			\item {Delivered concierge services, assisting guests with information about the hotel and the surrounding area.}
			\item {Bartended during evening hours, offering food services and ensuring a positive guest experience.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
\end{cventries}
